Dissecting Neural Style Transfer

### 2019-06-04 paper/paper.tex
Update on introduction by Jianzhen

\section{Literature Review}

>>>>

Image stylization is the process that mimics the appeal of artistic media [1] and converts input images into a stylized version. It is a research started with semi-automatic painting systems since 1990s [2] and can be used in many newly developed applications in machine learning and artificial intelligence [3]. This technique leads to a new form of communication [4]. With the use of image stylization, the media users can keep stylistic consistency on media platforms like Instagram or Twitter without obtaining skills in traditional artistic techniques [5]. Image stylization allows users to generate picture in traditional artistic styles, which had been expensive and time-consuming with traditional techniques [19]. It shifts the way how the media users share pictures on internet. At the beginning of the image stylization, which it started in 1980s, procedural filters and patch-based algorithms were studied and applied [4]. One example for the procedural filters is to refine image with strokes placement algorithms, which a grid of rendering brush strokes is placed over an image [12, 13]. Later on, patch-based synthesis was studied based on texture recognition [14]. Moreover, these two methods have numerous difficulties in further developments on the capture of complex nuances of an artist’s style, and can only work for certain types of images [4]. However, deep neural networks, which are developed as a general-purpose tool working different computer vision problems [15].  The paper published by Leon Gatys in 2015 has proven that a simple neural network works well on the texture recognition just like the patch-based synthesis algorithms [16]. 
One of the applications is auto-painter for cartoon image generation and it applies deep neural networks on image stylization [7]. These computational bio-inspired neural networks mimic the basic structure of brain neurons. Like the auto-painter, convolutional neural network is used in this paper for developing a tool in image stylization. Neural networks, especially for the deep artificial neural networks, has been widely studied and used in the pattern recognition and machine learning in recent years [8]. Convolutional neural network is one of the deep learning neural networks and have substantially achieved the state-of-the-art accuracies of object recognition [11]. This is the key in image stylization where the essential features in the style image are extracted and applied on the input image. 
This paper applies a pre-trained CNN, VGG-19, on image stylization and extends its possibilities on image stylization. CNNs have a similar structure as ordinary neural networks, which include neurons with learnable weights and biases. CNNs are typically feed-forward architecture and widely used in computer vision tasks in recent years [11]. Its basic unit is single neuron. Each of these neurons takes one or multiple inputs, conducts a dot product then optimally follows it with a non-linearity [9]. The core mathematical equation for CNN is a result derived from two functions by integration and this indicates how one’s shape is changed by the other. CNN works in a way similar to broad categorization [10]. When a CNN is used in image processing, every pixel of the input image will be processed by a feature detector and a feature map is given as the result. There will be very less, but critical features kept in the feature map compared to the input image. Consequently, some key features might be missed, and massive trainings are required for CNN’s accuracy on texture capture.

\section{Related Work}
